Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
Gather Sections 1 and 2 into a common section
comment on pitch invariance

@@

\section{Experiment 2}\label{sec:xp2}

@@

As explained in the first section, gathering perceptual similarity data is plagued is plagued with a size problem. Thus, the perceptual data considers 78 \ipts each represented by one sound recording, most often of C4 pitch and nuance mezzo forte. In order to provide enough data for the numerical analysis described in this section, we complement the data gathered during the second experiment as follows: for each \ipt, instead of one sound examplar we consider the whole range of nuance and pitch that is available. This leads to a dataset of 9346 sound recordings. It is thus assumed that the perceptual similarity is invariant with respect to pitch and nuance which is not necessarily true, but is taken in this paper as a reasonable assumption.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DATA COLLECTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Data collection}\label{sec:xp1}

%%%%%%%%%%%%%%%%%%%%%%%%% EXPERT JUDGMENTS OF PECULIARITY %%%%%%%%%%%%%%%%%%%%%%
\subsection{Expert judgments of technique peculiarities}

@@

%%%%%%%%%%%%%% CROWDSOURCED JUDGMENTS OF PAIRWISE SIMILARITY %%%%%%%%%%%%%%%%%%%%
\subsection{Crowdsourced judgments of pairwise similarity}

@@

As explained in the first section, gathering perceptual similarity data is plagued is plagued with a size problem. Thus, the perceptual data considers 78 \ipts each represented by one sound recording, most often of C4 pitch and nuance mezzo forte. In order to provide enough data for the numerical analysis described in this section, we complement the data gathered during the second experiment as follows: for each \ipt, instead of one sound examplar we consider the whole range of nuance and pitch that is available. This leads to a dataset of 9346 sound recordings. It is thus assumed that the perceptual similarity is invariant with respect to pitch and nuance which is not necessarily true, but is taken in this paper as a reasonable assumption.
\vl{It's too bad that this "reasonable" assumption is not challenged against the data. In music psychology, the "bandwidth for timbre invariance" is of the order of one octave (Handel and Erickson, Music Perception, 2001) or less (Steele and Williams, Music Perception, 2006).
One way to do it without collecting new similarity judgments would be to break down the precision by pitch of query.
Presumably we have an inverted U shape with a peak near C4.
#research #figure #biblio}
